{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-11-26 wacv_for_review.tex
Matrices and vectors represented in bold

The contribution of this paper is a novel, single-target tracking
algorithm running in a very high-speed, $\geq 300$ fps that deploys an
ensemble of KCFs, in turn, to more effectively address the scale
variance and the dynamic maneuver of a target while preserving
run-time performance as high as possible. We also developed a Bayes
filter to minimize any potential drifts while transiting one KCF to
another. In addition, we explore deep features with varying levels of
abstraction in the proposed {\it E}nKCF to improve tracking
performance and increase its flexibility being deployed on high-end,
single-board computer with GPUs.

@@

\textbf{Kernelized Correlation Filter} The Kernelized Correlation
Filter is a well-known single target tracking method and its work
flow has been detailed in other papers
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevant to this study. Its
computational efficiency is derived from the correlation filter
framework representing training examples as a circulant matrix. The
fact that a circulant matrix can be diagonalized by Discrete Fourier
transform is the key to reduce the complexity of any tracking method
based on correlation filter. The off-diagonal elements become zero
whereas the diagonal elements represent the eigenvalues of the
circulant matrix. The eigenvalues are equal to the DFT transformation
of the base sample ($x$) elements. The Kernelized Correlation Filter,
in particular, applies a kernel to $x$ to transform to a more
discriminative domain. The circulant matrix is then formed by applying
cyclic shifts on the kernelized $x$. Such kernelization operation
maintains O($nlog(n)$) complexity unlike other kernel algorithms
leading to O($n^{2}$) or even higher complexities.

The KCF solves essentially the problem of a regression in the form of
the regularization (ridge regression):
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
closed-form solution, an element-wise multiplication in
frequency domain was proposed for $\hat{w}$:
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
A non-linear version of this closed-form solution is proposed to increase robustness
to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized Fourier
domain dual form solution is expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\lambda$ represents the regularization weight whereas $\hat{k}^{xx}$ denotes
 the first row of the kernel matrix $K$ known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'})))
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $w$ and multi-channel features
such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
Specifically, one can execute an object detection task using this kernelized correlation
filter with multi-channel features as
\begin{equation}
r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
\end{equation}
where $r$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

@@

{\it YoungWoo : Particle filter smoothen the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}
\end{comment}  
As explained earlier, the {\it E}nKCF updates a target's translation
at every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead drifts at the
later frames. To prevent such potential drifts, we developed a Bayes
filter that incorporates a target's motion to smooth any intermediate
outputs from individual KCFs. In particular, we use a particle filter
to estimate the target's image coordinate based on the {\it E}nKCF's
outputs. The state in this paper, $X_t$, represents a target's pixel
coordinates and its velocity, $X_t = \lbrace x, y, v_{x}, v_{y}
\rbrace$, where $x$ and $y$ are the pixel coordinates of the target's
centroid, $v_x$ and $v_y$ are the velocity estimated along the
$x$-axis and $y$-axis. The particle filter predicts, using a constant
velocity motion model, a target's next state by generating a predefined
number of particles. Then it uses the confidence maps of {\it E}nKCF
as observation to update the state. The weight of a particle is
computed as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M} y_{R}(x_{t}-i,y_{t}-j)$,
where $w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$ and $M$ denote the
size of rows and columns of the confidence map. 
%Alternatively one can
%also use the Euclidean distance of particles to the location of
%maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

@@

\textbf{Finding Optimal Hyper-parameters} As each of three KCFs in
       {\it E}nKCF is designed to address specific challenges in
       single target tracking problem, the optimal parameters for
       individual KCFs should be different. We set the learning rates
       of individual filters, $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$
       differently as $0.020$, $0.020$ and $0.010$. For the kernel of
       the Gaussian neighboring function, we empirically found the
       optimal values of $\alpha$ as $0.7$, $0.6$, and $0.9$ for
       $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale filter
       update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
       ratio. The padding size for the correlation filters is tuned to
       $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
       $R_{s}$. For our particle filter implementation, we empirically
       set the number of particles to $1,000$ to balance the run-time
       performance and accuracy. To keep the level of variance among
       the particles reasonable, we performed the re-sampling only
       when the \textit{efficient number of samples}, ($ \hat{N}_{eff}
       \approx (\sum_{p=1}^{P}w_{p}^{2})^{-1} $), is lower than a
       pre-defined threshold.

>>>>

The contribution of this paper is a novel, single-target tracking
algorithm running in a very high-speed ($\geq300$ fps), that deploys an
ensemble of KCFs, in turn, to more effectively address the scale
variance and the dynamic maneuver of a target while preserving
run-time performance as high as possible. We also developed a Bayes
filter to minimize any potential drifts while transiting one KCF to
another. In addition, we explore deep features with varying levels of
abstraction in the proposed {\it E}nKCF to improve tracking
performance and increase its flexibility being deployed on high-end,
single-board computer with GPUs.

@@

\textbf{Kernelized Correlation Filter} The Kernelized Correlation
Filter is a well-known single target tracking method and its work
flow has been detailed in other papers
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevant to this study. Its
computational efficiency is derived from the correlation filter
framework representing training examples as a circulant matrix. The
fact that a circulant matrix can be diagonalized by Discrete Fourier
transform is the key to reduce the complexity of any tracking method
based on correlation filter. The off-diagonal elements become zero
whereas the diagonal elements represent the eigenvalues of the
circulant matrix. The eigenvalues are equal to the DFT transformation
of the base sample ($\mathbf{x}$) elements. The Kernelized Correlation Filter,
in particular, applies a kernel to $\mathbf{x}$ to transform to a more
discriminative domain. The circulant matrix is then formed by applying
cyclic shifts on the kernelized $\mathbf{x}$. Such kernelization operation
maintains O($nlog(n)$) complexity unlike other kernel algorithms
leading to O($n^{2}$) or even higher complexities.

The KCF solves essentially the problem of a regression in the form of
the regularization (ridge regression):
\begin{equation}
E(h) = \frac{1}{2}||\mathbf{y}-\sum_{c=1}^{C}\mathbf{h_{c}}*\mathbf{x_{c}}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||\mathbf{h_{c}}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $\mathbf{y}$ represents the desired continuous response whereas $\mathbf{h}$ and
$\mathbf{x_{c}}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
closed-form solution, an element-wise multiplication in
frequency domain was proposed for $\hat{w}$:
\begin{equation}
\mathbf{\hat{w}} = \mathbf{\hat{x}^{*}}*\mathbf{\hat{y}}(\mathbf{\hat{x}^{*}}*\mathbf{\hat{x}}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
A non-linear version of this closed-form solution is proposed to increase robustness
to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized Fourier
domain dual form solution is expressed as
\begin{equation}
\mathbf{\hat{\alpha}} = \mathbf{\hat{y}}(\mathbf{\hat{k}^{xx}}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\lambda$ represents the regularization weight whereas $\mathbf{\hat{k}^{xx}}$ denotes
 the first row of the kernel matrix $\mathbf{K}$ known as \textit{gram matrix} and it is expressed as
\begin{equation}
\mathbf{k^{xx^{'}}} = exp(-\dfrac{1}{\alpha^{2}}(||\mathbf{x}||^{2}+||\mathbf{x}^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\mathbf{\hat{x}_{c}}^{*}\odot \mathbf{\hat{x}_{c}}^{'})))
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $\mathbf{w}$ and multi-channel features
such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
Specifically, one can execute an object detection task using this kernelized correlation
filter with multi-channel features as
\begin{equation}
\mathbf{r(z)} = F^{-1}(\mathbf{\hat{k}^{xz}} \odot \mathbf{\hat{\alpha}})
\end{equation}
where $\mathbf{r}$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

@@

{\it YoungWoo : Particle filter smoothen the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}
\end{comment}  
As explained earlier, the {\it E}nKCF updates a target's translation
at every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead drifts at the
later frames. To prevent such potential drifts, we developed a Bayes
filter that incorporates a target's motion to smooth any intermediate
outputs from individual KCFs. In particular, we use a particle filter
to estimate the target's image coordinate based on the {\it E}nKCF's
outputs. The state in this paper, $\mathbf{X_t}$, represents the target's pixel
coordinates and its velocity, $\mathbf{X_t} = \lbrace x, y, v_{x}, v_{y}
\rbrace$, where $x$ and $y$ are the pixel coordinates of the target's
centroid, $v_x$ and $v_y$ are the velocity estimated along the
$x$-axis and $y$-axis. The particle filter predicts, using a constant
velocity motion model, a target's next state by generating a predefined
number of particles. Then it uses the confidence maps of {\it E}nKCF
as observation to update the state. The weight of a particle is
computed as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$,
where $w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$ and $M$ denote the
size of rows and columns of the confidence map. 
%Alternatively one can
%also use the Euclidean distance of particles to the location of
%maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

@@

\textbf{Finding Optimal Hyper-parameters} As each of three KCFs in
       {\it E}nKCF is designed to address specific challenges in
       single target tracking problem, the optimal parameters for
       individual KCFs should be different. We set the learning rates
       of individual filters, $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$
       differently as $0.020$, $0.020$ and $0.010$. For the kernel of
       the Gaussian neighboring function, we empirically found the
       optimal values of $\alpha$ as $0.7$, $0.6$, and $0.9$ for
       $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale filter
       update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
       ratio. The padding size for the correlation filters is tuned to
       $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
       $R_{s}$. For our particle filter implementation, we empirically
       set the number of particles to $1,000$ to balance the run-time
       performance and accuracy. To keep the level of variance among
       the particles reasonable, we performed the re-sampling only
       when the \textit{efficient number of samples}, ($ \hat{N}_{eff}
       \approx (\sum_{p=1}^{P}\mathbf{w}_{p}^{2})^{-1} $), is lower than a
       pre-defined threshold.
